Title Goes Here

### 2024-03-01 analysis/paper/paper.qmd
fix for 2023 year
new approach to tt/ntt ratio

year_ad_posted <- 
jobdata %>% 
  pull(url_to_data_source_e_g_paste_in_url_to_the_jobs_wiki_page) %>% 
  str_extract(.,  "[[0-9]]{4}-[[0-9]]{4}|2021-22") %>% 
  str_replace("2021-22",  "2021-2022")
 # fix for 2021-22 DONE!
 # fix for and 2023

@@

# ratio of tenure-track to untenured positions

base_url <- "http://academicjobs.wikia.com/wiki/Archaeology_Jobs_"

# starts at 2010-2011
# fix for 2021-22

years <- map_chr(2010:2019, ~str_glue('{.x}-{.x +1}'))
# though it seems to start at 2007-8: https://academicjobs.fandom.com/wiki/Archaeology_07-08

urls_for_each_year <- str_glue('{base_url}{years}')

@@

# what are the different sections? I reviewed every year to see what 
# headings were used to indicate TT and non-TT jobs
tt_sections <- c("TENURE-TRACK POSITIONS",
                "TENURE-TRACK OR TENURED / FULL-TIME POSITIONS",
               "Tenure-Track or Tenured / Full-time Position",
               "ASSISTANT PROFESSOR OR OPEN RANK",
               "TENURE TRACK ASSISTANT PROFESSOR OR OPEN RANK",
               "TENURED ASSOCIATE OR FULL PROFESSOR",
               "ASSOCIATE OR FULL PROFESSOR")

non_tt_sections <- c("NON-TENURE-TRACK POSITIONS", 
                     "VISITING POSITIONS / Limited-Term Appointments / Postdocs", 
                     "Visiting Positions / Limited-Term Appointments / Postdocs",
                     "VISITING POSITIONS / LIMITED TERM APPOINTMENTS / POSTDOCS",   
                     "VISITING POSITIONS / LIMITED-TERM APPOINTMENTS / POSTDOCS / PART-TIME POSITIONS",
                     "VISITING POSITIONS")

end_non_tt_sections <- c("DISCUSSION, RUMORS AND SPECULATION",   
                         "DISCUSSION, RUMORS, SPECULATION",
                         "General Discussion, Rumors, and Speculation" )

# what to do about this?
# "COMPLETED SEARCHES"

# this is a function that extracts text from each section with a heading
# that matches those above, and counts how many positions are in each section
library(stringr)
get_counts_tt_non_tt <- function(x){

tt_start      <- which(str_detect(x, 
                                  paste(tt_sections, 
                                        collapse = "|")))[1] 
non_tt_start   <- which(str_detect(x, 
                                   paste(non_tt_sections, 
                                         collapse = "|")))[1] 
non_tt_end    <- which(str_detect(x, 
                                  paste(end_non_tt_sections, 
                                        collapse = "|")))[1] 
n_tt_jobs     <- length( x[(tt_start + 1) : (non_tt_start - 1) ] )
n_non_tt_jobs <- length( x[(non_tt_start + 1) : (non_tt_end  - 1) ] )

return(list(n_tt_jobs = n_tt_jobs,
            n_non_tt_jobs = n_non_tt_jobs))
}

# calculate ratio
ratios_of_tt_to_non_tt_jobs <- 
map_df(urls_for_each_year_headers,
    get_counts_tt_non_tt) %>% 
  mutate(ratio = n_tt_jobs / n_non_tt_jobs) %>% 
  mutate(year = str_replace(str_sub( urls_for_each_year, -9),
                            "-", "-\n"))

# draw plot
  ggplot(ratios_of_tt_to_non_tt_jobs) +
  aes(year, 
      group = 1,
      ratio) +
  geom_line() +
  geom_hline(yintercept = 1,
             colour = "red") +
  labs(y = "Ratio of tenure-track to non-tenure track\njobs in Archaeology",
       x = "") +
  theme_bw(base_size = 16)

>>>>

year_ad_posted <- 
jobdata %>% 
  pull(url_to_data_source_e_g_paste_in_url_to_the_jobs_wiki_page) %>% 
  str_extract(.,  "[[0-9]]{4}-[[0-9]]{4}|2021-22") %>% 
  str_replace("2021-22",  "2021-2022")
 # fix for 2021-22 DONE!
 # fix for 2023 DONE!

@@

# ratio of tenure-track to untenured positions
# base URL changes after 2018_2019

base_url_to_2019 <- "https://academicjobs.fandom.com/wiki/Archaeology_Jobs_"
base_url_after_2020 <- "https://academicjobs.fandom.com/wiki/Archaeology_"

# starts at 2010-2011
# fix for 2021-22
# base UR

years_to_2019 <- map_chr(2010:2019, ~str_glue('{.x}-{.x +1}'))
years_after_2020 <- map_chr(2020:2023, ~str_glue('{.x}-{.x +1}'))
# though it seems to start at 2007-8: https://academicjobs.fandom.com/wiki/Archaeology_07-08

# make a set of URLs for each page for each year
urls_for_each_year <- c(str_glue('{base_url_to_2019}{years_to_2019}'), 
                        str_glue('{base_url_after_2020}{years_after_2020}')) %>% 
    str_replace("2021-2022", "2021-22")

@@

# keep only headings that are actual jobs, they include the terms:
job_headings <- c("college", "university")

total_number_of_jobs_per_year <- 
  map(urls_for_each_year_headers,
      ~str_subset(tolower(.x),
          paste0(job_headings, collapse = "|")))

total_number_of_jobs_per_year_n <- 
map_int(total_number_of_jobs_per_year, length)

total_number_of_jobs_per_year_tbl <- 
tibble(
  url_to_data_source_e_g_paste_in_url_to_the_jobs_wiki_page = urls_for_each_year,
  total_number_of_jobs_per_year = total_number_of_jobs_per_year_n
)

# count of TT jobs per year from our manual data collection,
# join with our total number of all jobs by scraping
count_of_tt_jobs_per_year_from_our_form <- 
jobdata %>% 
  group_by(url_to_data_source_e_g_paste_in_url_to_the_jobs_wiki_page) %>% 
  tally() %>% 
  left_join(total_number_of_jobs_per_year_tbl) %>% 
  rename(n_tt_jobs  = n,
         n_total_jobs = total_number_of_jobs_per_year) %>% 
  mutate(n_non_tt_jobs = n_total_jobs - n_tt_jobs,
         ratio_tt_2_ntt = n_tt_jobs / n_non_tt_jobs) %>% 
  mutate(year = str_extract(url_to_data_source_e_g_paste_in_url_to_the_jobs_wiki_page,  "[[0-9]]{4}-[[0-9]]{4}|2021-22")) %>%  
  mutate(year = ifelse(year =="2021-22",  "2021-2022", year))

# draw plot
  ggplot(count_of_tt_jobs_per_year_from_our_form) +
  aes(year, 
      group = 1,
      ratio_tt_2_ntt) +
  geom_line() +
  geom_hline(yintercept = 1,
             colour = "red") +
  labs(y = "Ratio of tenure-track to non-tenure track\njobs in Archaeology",
       x = "") +
  theme_bw(base_size = 16)
